Performance of Jellyfish Search Optimiser on Projection Pursuit Problems

### 2024-02-06 optim.qmd
some preliminary results of example 1

# Introduction [Nicolas and Jessica]

@@

# Projection pursuit, index functions and optimisation [Di and Sherry] {#sec-background}

# The jellyfish optimiser and property for good optimisers [Nicolas and Jessica] {#sec-theory}

@@

# Application [Di and Sherry] {#sec-simulation}

@@

Jellyfish optimiser, as a multi-start algorithm, is efficient in [...] for high-dimensional problems

@@

# Conclusion [Di and Sherry] {#sec-conclusion}

>>>>

```{r setup, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggplot2)
library(patchwork)
```

# Introduction \[Nicolas and Jessica\]

@@

# Projection pursuit, index functions and optimisation \[Di and Sherry\] {#sec-background}

# The jellyfish optimiser and property for good optimisers \[Nicolas and Jessica\] {#sec-theory}

@@

# Application \[Di and Sherry\] {#sec-simulation}

@@

Jellyfish optimiser, as a multi-start algorithm, is efficient in \[...\] for high-dimensional problems

```{r echo = FALSE}
load(here::here("data/pipe_better.rda"))
load(here::here("data/pipe_jellyfish.rda"))
```

```{r}
#| fig.width = 6,
#| fig.height = 3,
#| fig.align = "center",
#| fig.cap = "sthis sdfaksdlf"
pipe_better |>
  bind_rows(pipe_jellyfish) |>
  mutate(dim = as.factor(6 + (as.numeric(dim) - 1) * 2)) |>
  ggplot(aes(x = dim, y = index_val, group = interaction(optimiser, dim), color = optimiser)) +
  geom_violin(width = 2, adjust = 0.5, position = position_dodge(width = 0.4)) +
  ggbeeswarm::geom_quasirandom(size = 0.1, width = 0.1, dodge.width = 0.4) +
  theme_bw() +
  scale_y_continuous(breaks = seq(0.85, 1, 0.01)) +
  scale_color_brewer(palette = "Accent") + 
  labs(y = "Index", x = "Dimension")

```

```{r}
#| fig.width = 8,
#| fig.height = 5,
#| fig.align = "center",
#| fig.cap = "sthis sdfaksdlf"
get_proj <- function(data){
  quantiles <- map(1:4, ~data |>
                     filter(dim == .x) |>
                     pull(index_val) |>
                     quantile(seq(0, 1, 0.5), type = 3) |>
                     rev() |>
                     unname())

  res <- map2_dfr(
    unlist(quantiles),
    rep(1:4, each = 3),
    ~ data |>
      filter(dim == .y, index_val == .x) |>
      select(dim, proj, index_val),
    .id = "id"
    ) |>
    unnest(proj) |>
    mutate(index_val = sprintf("%.3f", index_val),
           optimiser = "jellyfish",
           id = (as.numeric(id) - 1) %%3 + 1,
           dim = as.factor(6 + (as.numeric(dim) - 1) * 2)) |>
    mutate(id = case_when(id == 1 ~ "best",
                          id == 2 ~ "mean",
                          id == 3 ~ "worst",
                          TRUE ~ "0thers"))
  return(res)
}

p1 <- get_proj(pipe_jellyfish)  |>
  ggplot(aes(x = V1, y = V2)) +
  geom_point(size = 0.1) +
  geom_text(data = ~. |> distinct(id, dim, index_val),
           aes(label = index_val), x =0, y = 3.7, size = 3) +
  facet_grid(dim ~ id) +
  xlim(-4, 4) + ylim(-4, 4) +
  theme_bw() +
  theme(aspect.ratio = 1, axis.ticks = element_blank(),
        axis.text = element_blank(), axis.title = element_blank(),
        panel.grid = element_blank())
p2 <- p1 %+% get_proj(pipe_better)
p1 + ggtitle("The Jellyfish Optimiser") | p2 + ggtitle("The Better Optimiser")

```

@@

# Conclusion \[Di and Sherry\] {#sec-conclusion}

### 2024-02-06 optim.tex
some preliminary results of example 1

\begin{keyword}
    projection pursuit \sep optimization \sep 
    jellyfish optimiser
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

>>>>

\begin{keyword}
    projection pursuit \sep optimization \sep 
    jellyfish optimiser
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{figure}

{\centering \includegraphics{optim_files/figure-pdf/unnamed-chunk-2-1.pdf}

}

\caption{sthis sdfaksdlf}

\end{figure}

\begin{figure}

{\centering \includegraphics{optim_files/figure-pdf/unnamed-chunk-3-1.pdf}

}

\caption{sthis sdfaksdlf}

\end{figure}
